\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-09-26 manuscript.tex
Modify title and author information in footer

\title{\LARGE \bf
Constrained Attitude Control on \( \SO \) }

@@

\makeAuthorInformation{
Manuscript received DATE; revised DATE; accepted DATE.
Shankar Kulumani, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,tylee\}@gwu.edu}

@@

\runningtitle{1}{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}{Constrained Attitude Control on \( \SO \) }

>>>>

\title{\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)} }

@@

\makeAuthorInformation{
Manuscript received DATE; revised DATE; accepted DATE.

Shankar Kulumani and Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 \texttt{ \{skulumani,tylee\}@gwu.edu}

@@

\runningtitle{1}{Shankar Kulumani and Taeyoung Lee}{Constrained Geometric Attitude Control on \( \SO \) }
